--- 
title: "Mathematical Behaviorism"
author: "David J. Cox (Ed.)"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: rstudio/bookdown-demo
description: "Mathematical models are practically used across all sciences to describe and predict the phenomena of which that science focuses on. This book catalogs and describes operant and respondent models of biological organismic behavior-environment relations."
---

# Prerequisites

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.name/tinytex/>.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```

<!--chapter:end:index.Rmd-->

# Introduction: Models and Math {#intro}

You can label chapter and section titles using `{#label}` after them, e.g., we can reference Chapter \@ref(intro). If you do not manually label them, there will be automatic labels anyway, e.g., Chapter \@ref(methods).

Figures and tables with captions will be placed in `figure` and `table` environments, respectively.

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

You can write citations, too. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [@xie2015].

<!--chapter:end:01-intro.Rmd-->

# Individual Neurons

## The Hodgkin-Huxley Model

## Hebbian Learning Rule

<!--chapter:end:02-individual-neurons.Rmd-->

# Aggregating Neural Events

## Neural Networks Modeling Choice

## Drift-Diffusion Models

## Q-Learning Algorithm

## Interval Timing Models

## Stimulus Discrimination


## Boilerplate template to keep while figuring out formatting
Math can be added in body using usual syntax like this 

$p$ is unknown but expected to be around 1/3. Standard error will be approximated

$$
SE = \sqrt(\frac{p(1-p)}{n}) \approx \sqrt{\frac{1/3 (1 - 1/3)} {300}} = 0.027
$$

You can also use math in footnotes like this^[where we mention $p = \frac{a}{b}$].

We will approximate standard error to 0.027[^longnote]

[^longnote]: $p$ is unknown but expected to be around 1/3. Standard error will be approximated

    $$
    SE = \sqrt(\frac{p(1-p)}{n}) \approx \sqrt{\frac{1/3 (1 - 1/3)} {300}} = 0.027
    $$

<!--chapter:end:03-aggregating-neural-events.Rmd-->

# Individual Behavior

Some _significant_ applications are demonstrated in this chapter.

## Competition to Gain Association Models

## Rescorla-Wagner Model

## Attention Models
### Mackintosh

### Pearce-Hall

## Behavioral Momentum

## Matching Equations

## Discounting Equations

## Demand Equations

## Carrying Experiences Through Time
### Temporal Weighting Rule

## Combining Models
### Resurgence as Choice

<!--chapter:end:04-individual-behaviors.Rmd-->

# Aggregating Individual Behaviors

Some _significant_ applications are demonstrated in this chapter.

## Mathematical Principles of Reinforcement

## Evolutionary Theory of Behavioral Dynamics

## A-Learning

<!--chapter:end:05-aggregating-individual-behaviors.Rmd-->

# Group Behavior

Some _significant_ applications are demonstrated in this chapter.

## Static Models
### Social network models

### Ideal free distribution

## Dynamic Models
### Game Theory

### Agent-Based Modeling and Simulations

### Swarm Dynamics and Insect-Inspired Models


<!--chapter:end:06-group-behavior.Rmd-->

# Aggregating Group Behavior

Some _significant_ applications are demonstrated in this chapter.

## Static Models

## Dynamic Models
### Dynamic state models

### Diffusive and nondiffusive population models

### Multispecies eco-evolutionary models

<!--chapter:end:07-aggregating-group-behavior.Rmd-->

# Final Words

We have finished a nice book.

<!--chapter:end:08-summary.Rmd-->

`r if (knitr:::is_html_output()) '
# References {-}
'`

<!--chapter:end:09-references.Rmd-->

